Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)

### 2017-02-15 csf-2017/paper.tex
Refer to Akram's master thesis.

\begin{itemize}
\item \cite{akram_el-korashy_formal_2016}
\end{itemize}

>>>>

El-Korashy also defined a formal model of a capability machine, namely CHERI,
and uses it to prove a compartmentalization
result~\citep{akram_el-korashy_formal_2016} (not implying control flow
correctness). He also proves soundness of control-flow integrity (see above)
adapted to the capability machine, a result that seems orthogonal to the fact
that the machine uses capabilities.
